---
title: "Gov 50 Final Project"
author: "Alma Conway"
description: "Milestone 3"
output:
  distill::distill_article:
    self_contained: false
---


``` {r}

library(tidyverse) 


library(dplyr)

danishpolls <- read_csv("index_files/polls.csv")
danishpolls
remotes::install_github("MansMeg/SwedishPolls", subdir = "RPackage")
Swedishpolls <- SwedishPolls::get_polls()



```



```{r}
DPY <- danishpolls |>
  filter(year == c(2016, 2019, 2021)) 

DPY|>
  ggplot(aes(x = party_a)) +
  geom_bar()


```

```{r}
library(rjson)
```

```{r}
data <- fromJSON(file="LABO30_20221109-001127.json")

json_data <- as.data.frame(data)
print(json_data)
```
```{r}
as.data.frame(data$dataset$dimension)
```
```{r}
data$data
```


 
58
```{r, warning=FALSE}
labo31 <- data.frame(to = rep(NA, n), from = rep(NA, n), unemployment = rep(NA, n), year = rep(NA, n), y2029 = rep(NA,n), backg = rep(NA, n))
n = length(data$data)
 

for(i in 1:n){
  new_i = as.double(data$data[[i]]$values[1])
  
  new_row = c(data$data[[i]]$key[1], data$data[[i]]$key[2], new_i, data$data[[i]]$key[4], data$data[[i]]$key[6], data$data[[i]]$key[3])

  labo31[i,] = new_row
  }

labo32 <- as_tibble(labo31) 

```
 

new_i = as.double(data$data[[i]]$values[1])
 

    new_row = c(data$data[[i]]$key[1], data$data[[i]]$key[2], new_i, data$data[[i]]$key[4], data$data[[i]]$key[6], data$data[[i]]$key[3])

    labo31[i,] = new_row
 

immcountry <- data.frame(age=rep("age", n), to = rep("reporting country", n), from = "country background", yearsofunemployment = "time")
 

LABO30: Proportion of the population who does not work or study (per cent) by reporting country, country background, population category, time, sex and age
 

x = year

```{r}
 

labo32 |>
  ggplot(aes(x = year)) +geom_boxplot(aes(y= unemployment))

labo31 = na.omit(labo31)
 
labo31

aex(x =unemployment)

labo31$unemployment = as.numeric(labo31$unemployment)
 
labo31
new_i = as.double(data$data[[i]]$values[1])
    
    new_row = c(data$data[[i]]$key[1], data$data[[i]]$key[2], new_i, data$data[[i]]$key[4], data$data[[i]]$key[6], data$data[[i]]$key[3])
    
    labo31[i,] = new_row
immcountry <- data.frame(age=rep("age", n), to = rep("reporting country", n), from = "country background", yearsofunemployment = "time")

```
 
LABO30: Proportion of the population who does not work or study (per cent) by reporting country, country background, population category, time, sex and age


x = year

labo |>
ggplot(aes(x = year)) +
geom_boxplot(aes(y= unemployment))


```{r}
labo = na.omit(labo)
labo
```
```{r}
#aex(x =unemployment)
```


```{r}
labo31$unemployment = as.numeric(labo31$unemployment)

labo31

hw <- labo31 |>
  filter(y2029 =="2029Y", backg == "FBTWOFBP", from =="AFR") |> 
ggplot( mapping = aes(x = to, y = unemployment)) +
  geom_boxplot(color = "darkorchid3") +
  labs(x= "Receiving Country", y= "Proportion of the population who does not work or study", title = "Denmark v Sweden Unemployment Rate of immigrants from Africa") 
hw


```
who are Foreign born with two foreign born parents
 ggplot( data = labo, mapping = aes(x = year, y = unemployment))

      	2016	2017	2018
Denmark	51.7	46.0	39.2
Sweden	47.0	40.5	34.4

```{r}
data <- data.frame( Denmark = c(51.7, 46, 39.2), Sweden =c(47, 40.5, 34.4), row.names = c(2016,2017,2018)) 

  
ggplot(data = data, mapping = aes(x = c(2016,2017,2018)))


```


```


  group_by(c(
dest_country, year)) |>

 group_by(dest_country) |>
 
 + geom_smooth(color = "indianred1") 



```{r, setup}
library(tidyverse)
library(infer)

alma <- read_csv("alma.csv")

```

```{r}
head(alma)
```


 
```{r}
 visualization <- alma |> 
  filter(origin == "Africa") |> 
  ggplot(aes(x = `year`, y = `fb_pct_2par`)) +
  geom_point(mapping = aes(color = `dest_country`)) +
  labs(y = "Unemployment as Proportion / 100", title = "Sweden vs Denmark Proportion of youth immigrant population who does not work or study")

visualization

```


